quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Add the section Creating the coordinates of the hexagons

>>>>

Following the generation of hexagonal centroids, the `gen_hex_coord()` function constructs the coordinates of each hexagonal bin by defining its six polygonal vertices. These coordinates are used to visualize the hexagonal tessellation.

Each hexagon is defined relative to its centroid $(C_x, C_y)$, with six vertices positioned equidistantly around the center. The function first verifies the presence of the required hexagon width parameter `a1`. This width determines the horizontal spacing.

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as $dx = \frac{a_1}{2}$, and $dy = \frac{a_1}{\sqrt{3}}$ repectively. A vertical spacing factor $v = \frac{a_1}{2\sqrt{3}}$ refines vertical placement in staggered rows.

With these values, the function determines fixed offsets in the x and y directions for all six vertices relative to the centroid. These offsets form two vectors (`x_add_factor` and `y_add_factor`) corresponding to the six compass directions used to define the polygon shape: top, top-left, bottom-left, bottom, bottom-right, and top-right.

For each centroid, six vertices are computed and assigned a polygon ID (`hex_poly_id`) corresponding to the centroid’s `hexID`. These points are aggregated into a tibble that includes the polygon ID (`hex_poly_id`) and the respective x (`x`) and y (`y`) coordinates for all hexagon corners.

### 2025-05-12 paper-quollr.tex
Add the section Creating the coordinates of the hexagons

>>>>

Following the generation of hexagonal centroids, the \texttt{gen\_hex\_coord()} function constructs the coordinates of each hexagonal bin by defining its six polygonal vertices. These coordinates are used to visualize the hexagonal tessellation.

Each hexagon is defined relative to its centroid \((C_x, C_y)\), with six vertices positioned equidistantly around the center. The function first verifies the presence of the required hexagon width parameter \texttt{a1}. This width determines the horizontal spacing.

Two derived constants are calculated to define the relative distances to the vertices. The horizontal and vertical offset is defined as \(dx = \frac{a_1}{2}\), and \(dy = \frac{a_1}{\sqrt{3}}\) repectively. A vertical spacing factor \(v = \frac{a_1}{2\sqrt{3}}\) refines vertical placement in staggered rows.

With these values, the function determines fixed offsets in the x and y directions for all six vertices relative to the centroid. These offsets form two vectors (\texttt{x\_add\_factor} and \texttt{y\_add\_factor}) corresponding to the six compass directions used to define the polygon shape: top, top-left, bottom-left, bottom, bottom-right, and top-right.

For each centroid, six vertices are computed and assigned a polygon ID (\texttt{hex\_poly\_id}) corresponding to the centroid's \texttt{hexID}. These points are aggregated into a tibble that includes the polygon ID (\texttt{hex\_poly\_id}) and the respective x (\texttt{x}) and y (\texttt{y}) coordinates for all hexagon corners.
